Discovery of s-process stars in the LAMOST survey

### 2018-01-25 article/ms.tex
methods

\subsubsection{Further enhancements}
We undertook an identical analysis to the process described in Section \ref{sec:cand} for sodium, technetium, and carbon enhancement. We filtered for negative residuals in the enhanced sodium doublet lines 5889.950\AA\hspace{0.2mm} and 5895.924\AA. Our analysis produced 5 matches with our Barium star candidates. 51 canditdates were discovered to be enhanced in a single technetium line. And, for the CH and G band region at approximately 4300\AA\hspace{0.2mm} we matched 178 enhanced stars out of our total 257 stars.

>>>>

\subsubsection{Enhancements due to sodium, technetium, and carbon}
We performed an identical analysis to the process described in Section \ref{sec:cand} in order to identify sodium, technetium, or carbon enhancement in our sample of 257 Barium stars. We used the sodium doublet lines at 5889\,\AA\ and 5895\,\AA\ to select Barium stars enhanced in sodium, and required significant absorption in both features. Only 5/257 Barium stars met this criteria,  \todo{however something about the dust for those stars}. For technetium enhancement we searched for significant residual deviations at the 4049\,\AA, 4238\,\AA, 4262\,\AA, 4297\,\AA, and 5924\,\AA. These absorption lines are extremely weak, and would require a substantial amount of technetium before it would be visible in a high S/N LAMOST spectrum. We found 51 Barium stars exhibited some level of significant enhancement (based on the filters above) at a single technetium line, yet none showed enhancement at more than one technetium line. We note that the single enhancement near technetium for these 51 stars may be the consequence of data reduction/calibration artefacts, but we include details of which stars matched on technetium in Table \ref{tab:table} nonetheless.
Finally, for carbon enhancement we searched for significant deviations at the CH and G band near 4300\,\AA. We found 178/257 stars to show significant carbon enhancement (e.g., $[\textrm{C/M}] \gtrsim 0.5$).
